A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-19 main.Rmd
done with 5.1

The prime force that drives the software's design choices is "data". All functions in **tsibble** starts with `data` or its variants as the first argument, namely "data first". They work naturally with the pipe operator `%>%`, read as "then". This not only lays out a consistent interface but also addresses the significance of the data throughout the software.

Beyond the tools, the print display provides a quick and comprehensive glimpse of data in temporal context, particularly useful when handling a large collection of data. Below conveys the pieces of critical and contextual picture about the data in Table \ref{tab:tb-sub}: (1) data dimension with its shorthand time interval, alongside time zone if date-times; (2) variables that constitute of the "key" with the number of series. These details aid users in understanding their data better and manipulate the data with care.

>>>>

The prime force that drives the software's design choices is "data". All functions in **tsibble** start with `data` or its variants as the first argument, namely "data first". They work naturally with the pipe operator `%>%`, read as "then". This not only lays out a consistent interface but also addresses the significance of the data throughout the software.

Beyond the tools, the print display provides a quick and comprehensive glimpse of data in temporal context, particularly useful when handling a large collection of data. The  contextual summary provided by the print function on the data is shown in Table \ref{tab:tb-sub} contains (1) data dimension with its shorthand time interval, alongside time zone if date-time, (2) variables that constitute the "key" with the number of series. These details aid users in understanding their data better.
